19Q2

### 2020-01-08 19Q2.Rmd

@@

@@

```{r fig.height=8, fig.width=15, eval=FALSE}
ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "mutation", legend_title = "CCLE -log10(p-value)", legend_breaks = seq(0, 12, by = 3), row_names = FALSE, color = "darkgreen", col_title = "", row_title_txt = "Genes", radius = 0.023)
ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "mutation", legend_title = "CTRP -log10(p-value)", legend_breaks = seq(0, 18, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.008)
ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "mutation", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Genes", radius = 0.011)
ht_crispr2 <- MakeWilcoxonHeatmap(signif_df = filter(crispr_signif_g2p_g, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "crispr", legend_title = "CRISPR -log10(p-value)", legend_breaks = seq(0, 45, by = 9), row_names = TRUE, color = "darkorchid4", col_title = "", row_title_txt = "Genes", radius = 0.15)
ht_mut_list <- ht_crispr2 + ht_ccle2 + ht_ctrp2 + ht_gdsc2
lgd <- list(Legend(labels = c("Resistance", "Sensitivity", "p < 0.05"), type = "points", pch = c(21, 21, 8), nrow = 1, background = "white", legend_gp = gpar(col = "black", fill = c("red", "white"))))
ht_mut_grob <- grid.grabExpr(draw(ht_mut_list, gap = unit(0.25, "in"), heatmap_legend_side = "top", annotation_legend_list = lgd, annotation_legend_side = "top", merge_legend = TRUE))

crispr_signif_g2p_dg_summ <- filter(crispr_signif_g2p_g, InG2P == "Yes") 
ccle_signif_g2p_dg_summ <- filter(ccle_signif_g2p_dg, InG2P == "Yes") 
ctrp_signif_g2p_dg_summ <- filter(ctrp_signif_g2p_dg, InG2P == "Yes") 
gdsc_signif_g2p_dg_summ <- filter(gdsc_signif_g2p_dg, InG2P == "Yes")

@@

```{r prot_changes, eval = FALSE, fig.height=15, fig.width=15}
ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = ccle_signif_prot_4plot, feature = "protein changes", legend_title = "CCLE -log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = FALSE, color = "darkgreen", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.021)
ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = ctrp_signif_prot_4plot, feature = "protein changes", legend_title = "CTRP -log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.012)
ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = gdsc_signif_prot_4plot, feature = "protein changes", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 8, by = 2), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.0125)
ht_crispr2 <- MakeWilcoxonHeatmap(signif_df = crispr_signif_prot_4plot, feature = "protein changes CRISPR", legend_title = "CRISPR -log10(p-value)", legend_breaks = seq(0, 25, by = 5), row_names = TRUE, color = "darkorchid4", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.135)
ht_prot_list <- ht_crispr2 + ht_ccle2 + ht_ctrp2 + ht_gdsc2
lgd <- list(Legend(labels = c("Resistance", "Sensitivity", "p < 0.05"), type = "points", pch = c(21, 21, 8), nrow = 1, background = "white", legend_gp = gpar(col = "black", fill = c("red", "white"))))
ht_prot_grob <- grid.grabExpr(draw(ht_prot_list, gap = unit(0.25, "in"), heatmap_legend_side = "top", annotation_legend_list = lgd, annotation_legend_side = "top", merge_legend = TRUE))

@@

## CN/GE

```{r CN_GE, eval = FALSE, fig.height=10, fig.width=15}
# Copy number

@@

## First draft figures

>>>>

ccle_unique <- unique(ccle) # Pre: 1512092
ctrp_unique <- unique(ctrp) # Pre: 47807047
gdsc_unique <- unique(gdsc) # Pre: 10143182

@@

## DUPLICATES

```{r}
# All nrow = 0
# crispr_prot_dup <- crispr_prot[duplicated(crispr_prot),]
# ccle_prot_dup <- ccle_prot[duplicated(ccle_prot),]
# ctrp_prot_dup <- ctrp_prot[duplicated(ctrp_prot),]
# gdsc_prot_dup <- gdsc_prot[duplicated(gdsc_prot),]

```

@@

## Mutation status figure

```{r}
crispr_g2p_count <- filter(crispr_signif_g2p_g, Gene %in% unique(g2p_mut$Gene), InG2P == "Yes")
ccle_g2p_count <- filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene), InG2P == "Yes")
ctrp_g2p_count <- filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene), InG2P == "Yes")
gdsc_g2p_count <- filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene), InG2P == "Yes")
```

```{r mut_status_fig, fig.height=8, fig.width=15, eval=FALSE}
ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "mutation", legend_title = "CCLE -log10(p-value)", legend_breaks = seq(0, 12, by = 3), row_names = FALSE, color = "darkgreen", col_title = "", row_title_txt = "Genes", radius = 0.023)
ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "mutation", legend_title = "CTRP -log10(p-value)", legend_breaks = seq(0, 18, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes", radius = 0.008)
ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "mutation", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 5, by = 1), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Genes", radius = 0.011)
ht_crispr2 <- MakeWilcoxonHeatmap(signif_df = filter(crispr_signif_g2p_g, Gene %in% unique(g2p_mut$Gene) & Mutation_1_count >= 3), feature = "crispr", legend_title = "CRISPR -log10(p-value)", legend_breaks = seq(0, 45, by = 9), row_names = TRUE, color = "darkorchid4", col_title = "", row_title_txt = "Genes", radius = 0.15)
ht_mut_list <- ht_crispr2 + ht_ccle2 + ht_ctrp2 + ht_gdsc2
lgd <- list(Legend(labels = c("Resistance", "Sensitivity", "p < 0.05"), type = "points", pch = c(21, 21, 8), nrow = 1, background = "white", legend_gp = gpar(col = "black", fill = c("red", "white"))))
ht_mut_grob <- grid.grabExpr(draw(ht_mut_list, gap = unit(0.25, "in"), heatmap_legend_side = "top", annotation_legend_list = lgd, annotation_legend_side = "top", merge_legend = TRUE))

crispr_signif_g2p_dg_summ <- filter(crispr_signif_g2p_g, InG2P == "Yes") 
ccle_signif_g2p_dg_summ <- filter(ccle_signif_g2p_dg, InG2P == "Yes") 
ctrp_signif_g2p_dg_summ <- filter(ctrp_signif_g2p_dg, InG2P == "Yes") 
gdsc_signif_g2p_dg_summ <- filter(gdsc_signif_g2p_dg, InG2P == "Yes") q

@@

## Protein changes figure

```{r}
test2 <- select(g2p_prot, Direction_Curated, Gene,Gene_Protein_Change) %>% drop_na(Direction_Curated) %>% unique()
unique(test2$Gene)

crispr_g2p_prot<- filter(crispr_signif_prot, Gene_Protein_Change %in% unique(g2p_prot$Gene_Protein_Change), InG2P == "Yes")
ccle_g2p_prot <- filter(ccle_signif_prot, Drug_Gene_Protein_Change %in% unique(g2p_prot$Drug_Gene_Protein_Change), InG2P == "Yes")
sum(!is.na(ccle_g2p_prot$p))
ctrp_g2p_prot <- filter(ctrp_signif_prot, Drug_Gene_Protein_Change %in% unique(g2p_prot$Drug_Gene_Protein_Change), InG2P == "Yes")
sum(!is.na(ctrp_g2p_prot$p))
gdsc_g2p_prot <- filter(gdsc_signif_prot, Drug_Gene_Protein_Change %in% unique(g2p_prot$Drug_Gene_Protein_Change), InG2P == "Yes")
sum(!is.na(gdsc_g2p_prot$p))
```

```{r prot_changes_fig, eval = FALSE, fig.height=15, fig.width=15}
ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = ccle_signif_prot_4plot, feature = "protein changes", legend_title = "CCLE -log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = FALSE, color = "darkgreen", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.021)
ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = ctrp_signif_prot_4plot, feature = "protein changes", legend_title = "CTRP -log10(p-value)", legend_breaks = seq(0, 15, by = 3), row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.012)
ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = gdsc_signif_prot_4plot, feature = "protein changes", legend_title = "GDSC -log10(p-value)", legend_breaks = seq(0, 8, by = 2), row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.0125)
ht_crispr2 <- MakeWilcoxonHeatmap(signif_df = crispr_signif_prot_4plot, feature = "protein changes CRISPR", legend_title = "CRISPR -log10(p-value)", legend_breaks = seq(0, 25, by = 5), row_names = TRUE, color = "darkorchid4", col_title = "", row_title_txt = "Gene:Protein Change", na_color = "black", radius = 0.135)
ht_prot_list <- ht_crispr2 + ht_ccle2 + ht_ctrp2 + ht_gdsc2
lgd <- list(Legend(labels = c("Resistance", "Sensitivity", "p < 0.05"), type = "points", pch = c(21, 21, 8), nrow = 1, background = "white", legend_gp = gpar(col = "black", fill = c("red", "white"))))
ht_prot_grob <- grid.grabExpr(draw(ht_prot_list, gap = unit(0.25, "in"), heatmap_legend_side = "top", annotation_legend_list = lgd, annotation_legend_side = "top", merge_legend = TRUE))

@@

## CN/GE figure

```{r CN_GE_fig, eval = FALSE, fig.height=10, fig.width=15}
# Copy number

@@

Fusions are completely driven by HL lineage: HL cell lines are the only cell lines that contain ABL1-BCR, BCR-ABL1, and PML-PARA fusions.
```{r}
test <- unique(select(fus, disease, FusionPair, Fusion_Status)) %>% filter(Fusion_Status == "Yes")
test
```

## Lineages

Mutation:
```{r}
crispr_mut_lin <- filter(crispr_signif_lin, InG2P == "Yes")
ccle_mut_lin <- filter(ccle_signif_dgl, InG2P == "Yes")
ctrp_mut_lin <- filter(ctrp_signif_dgl, InG2P == "Yes")
gdsc_mut_lin <- filter(gdsc_signif_dgl, InG2P == "Yes")
```

```{r}
crispr_test <- filter(crispr, Gene_Lin == "PTCH1_skin")
ggplot(crispr_test, aes(x = as.character(Mutation), y = Score)) +
  geom_boxplot() +
  geom_point() +
  stat_compare_means(method = "wilcox", aes(label = paste0("p = ", ..p.format..)), label.x = 1.35)
```

```{r}
crispr_Dup <- crispr[duplicated(crispr),]
ccle_Dup <- ccle[duplicated(ccle),]
```

## OLD: First draft figures
